---
title: "PredictSoilC with PCA result"
author: "Emily Lacroix"
date: "25 APR 2024"
output: 
  github_document:
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set-up

## Load libraries

```{r message=FALSE}

library(MASS)
library(MuMIn)
library(car)
library(vegan)
library(psych)
library(readxl)
library(nlme)
library(outliers)
library(tidyverse)

conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")


```

## Figure theme
```{r}
my_theme <- function(base_size = 13, base_family = ""){ ## Control base font face and size. use `rel()` for relative font size.
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.border = element_rect(colour = "black", fill = "transparent"),
      panel.background  = element_blank(),
      panel.grid = element_blank(),
      strip.background = element_blank(),
      strip.text = element_text(size = 11),
      strip.text.y = element_text(size = 11)
    )
}

```

## Labels
```{r}

site_labels <- 
  c(
    "CREC" = "Carrington, ND",
    "GR" = "Novelty, MO",
    "SM" = "Crossville, AL",
    "WO" = "Wooster, OH"
  )

till_labels <- 
  c(
    "UN" = "Uncultivated",
    "NT" = "No-till",
    "MT" = "Minimum till",
    "CT" = "Conventional till"
  )

```

## File names

```{r eval=FALSE}

all_data_excel <- "AllData_FINAL.xlsx"

anaerobe_file <- "anaerobe_pca.csv"

```

```{r eval=TRUE, echo=FALSE}

all_data_excel <- "/Users/elacroi3/Documents/Research/SHI/Data/DataCompilation/AllData_FINAL.xlsx"

anaerobe_file <- "anaerobe_pca.csv"

```

## Import
```{r message=FALSE}

anaerobes_by_pca <- anaerobe_file %>%  read_csv()

mineral <- 
  all_data_excel %>% 
  read_xlsx(sheet = "mineral_protection") %>% 
  select(-c(ssa_analysis_date)) %>% 
  separate(sample, into = c("site", "till", "amend", "rep")) %>% 
  mutate(
    landscape_position = if_else(site == "GR", amend, NA_character_),
    across(amend, ~if_else(site == "GR", "U", .)),
    across(rep, as.numeric)
  )

climate <- 
  all_data_excel %>% 
  read_xlsx(sheet = "climate", na = "NA") %>% 
  rename(rep = field_rep)


root_mass_bd <-
  all_data_excel %>% 
  read_xlsx(sheet = "gravimetric", na = "NA") %>% 
  mutate(
    avg_plant_mass_per_cm3 = plant_mass_2_mm / volume_cm3
  ) %>% 
    group_by(site, till, amend, landscape_position, field_rep) %>% 
    summarise(
      avg_plant_mass_per_cm3 = mean(avg_plant_mass_per_cm3, na.rm = TRUE),
      avg_bd = mean(bd, na.rm = TRUE)
    ) %>% 
  rename(rep = field_rep)


c_n <- 
  all_data_excel %>% 
  read_xlsx(sheet = "c_n", na = "NA") %>%
  rename(
    amend = amend_pos,
    rep = field_rep
  ) %>% 
  mutate(
    landscape_position = if_else(site == "GR", amend, NA_character_),
    across(amend, ~if_else(site == "GR", "U", .)),
  )

aggregate_est <- 
  all_data_excel %>% 
  read_xlsx(sheet = "agg_est") %>% 
  select(site, till, amend, landscape_position, rep, wsa_perc)


```


## Join it all together 

This data:

* combines all of the imported data
* removes the WO-UN-U-2 outlier (which was also removed from `ddPCR.Rmd`)
* removes GR samples that have incomplete anaerobe abundances due to droplet generation errors for select genes

```{r}

all_data <- 
  mineral %>% 
  inner_join(
    anaerobes_by_pca,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    climate,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    root_mass_bd,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    c_n,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 

  left_join(
    aggregate_est,
    by = c("site", "till", "amend", "landscape_position", "rep")  
  ) %>% 
  rowid_to_column() %>% 
  arrange(site, till, amend, landscape_position, rep) %>% 
  ungroup() %>% 
  select(-landscape_position) %>% 
  na.omit() %>% 
  mutate(
    across(till, ~factor(., levels = c("UN", "NT", "MT", "CT"))),
    across(amend, ~factor(., levels = c("U", "A"))),
  )


```


# PC anaerobe copies vs. Soil C

## All sites

### Create tibble

```{r}

multiple_reg_data_c <-
  all_data %>% 
  mutate(
    cultivated = if_else(till == "UN", 0, 1),
    amended = if_else(amend == "A", 1, 0),
    red_no_till = if_else(till %in% c("NT", "MT"), 1, 0),
  ) %>% 
  select(
    -c(
      rowid, 
      sample, 
      amend,
      contains(c("dsrAB", "gltA", "mcrA", "nirK", "nirS")),
      #pc1_values,
      soil_order,
      rep,
      gdd0,
      gdd10,
      precip_in_7,
      precip_in_14,
      precip_in_10,
      al_mmol_kg,
      fe_mmol_kg,
      mn_mmol_kg,
      plant_avail_n_ppm,
      npoc_mg_c_g_soil,
      avg_perc_n, #just playing around with removal
      map_mm, #removed after inspecting for VIF > 5
      mean_wfps  #removed after inspecting for VIF > 5
      )
  )

```
### Simple linear regression

#### Supplementary Figure S6a

```{r message=FALSE}

all_data %>% 
  mutate(
    across(till, ~factor(., labels = till_labels)),
    across(site, ~factor(., labels = site_labels))
  ) %>% 
  ggplot(aes(x = pc1_values, y = avg_perc_c)) + 
  geom_smooth(method = "lm", se = FALSE, color = "darkgray", linetype = 1) +
  geom_point(aes(color = site, shape = till), size = 4) +
  scale_color_brewer(palette = "RdYlBu") +
  scale_x_reverse() +
  my_theme() + 
  theme(
    aspect.ratio = 1,
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title.x = element_text(margin = margin(t = 8), size = 14),
    axis.title.y = element_text(margin = margin(r = 12), size = 14),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "top",
    legend.box = "vertical"
  ) +
  labs(
    y = "Organic Carbon (%)",
    x = "PC1 - Anaerobe Abundance",
    shape = "Agricultural Use and Till",
    color = NULL
  )

```

#### Statistics - Supplementary Figure S6a

```{r}
anaerobe_c <- lm(avg_perc_c ~ pc1_values, data = multiple_reg_data_c)

summary(anaerobe_c)
```

### Mixed-effects model - Unpublished

```{r}

anaerobe_c_mixed_effects <-   
  lme(avg_perc_c ~ pc1_values_trans, 
      random = ~1|site, 
      data = multiple_reg_data_c
  )

summary_mixed_effects <- anaerobe_c_mixed_effects %>% summary()

summary_mixed_effects$tTable

r.squaredGLMM(anaerobe_c_mixed_effects)

```
## Single Sites

### regressions WITH outlier in SM

#### Supplementary Figure S6b-e

```{r message=FALSE}
all_data %>% 
  mutate(
    across(till, ~factor(., labels = till_labels)),
    across(site, ~factor(., labels = site_labels))
  ) %>% 
  ggplot(aes(x = pc1_values, y = avg_perc_c)) + 
  geom_smooth(method = "lm", se = FALSE, color = "darkgray", linetype = 1) +
  geom_point(aes(color = site, shape = till), size = 4) +
  scale_color_brewer(palette = "RdYlBu") +
  scale_x_reverse() +
  facet_wrap(facets = vars(site), scales = "free") +
  my_theme() + 
  theme(
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    axis.title.x = element_text(margin = margin(t = 8), size = 16),
    axis.title.y = element_text(margin = margin(r = 12), size = 16),
    strip.text = element_text(size = 16),
    legend.position = "none",
    aspect.ratio = 1,
    
  ) +
  labs(
    y = "Organic Carbon (%)",
    x = "PC1 - Anaerobe Abundance",
    shape = "Agricultural Use and Till",
    color = NULL
  )

#ggsave("~/Desktop/PC_regression_by_site_no-line.png", dpi = 300)


```

#### Statistics - Supplementary Figure S6d

```{r}
anaerobe_c_crec <- 
  lm(
    avg_perc_c ~ pc1_values_trans, 
    data = all_data %>% filter(site == "CREC")
  )

anaerobe_c_wo <-
    lm(
    avg_perc_c ~ pc1_values_trans, 
    data = all_data %>% filter(site == "WO")
  )

anaerobe_c_gr <- 
    lm(
    avg_perc_c ~ pc1_values_trans, 
    data = all_data %>% filter(site == "GR")
  )

anaerobe_c_sm <-
    lm(
    avg_perc_c ~ pc1_values_trans, 
    data = all_data %>% filter(site == "SM" )
  )

summary(anaerobe_c_crec)
summary(anaerobe_c_wo)
summary(anaerobe_c_gr)
summary(anaerobe_c_sm)


```

### regressions WITHOUT outlier in SM

#### Figure - unpublished 
```{r message=FALSE}

all_data %>% 
  filter(!(site == "SM" & till == "UN" & rep == 3)) %>% 
  mutate(
    across(till, ~factor(., labels = till_labels)),
    across(site, ~factor(., labels = site_labels))
  ) %>% 
  ggplot(aes(x = pc1_values, y = avg_perc_c)) + 
  geom_smooth(method = "lm", se = FALSE, color = "darkgray", linetype = 1) +
  geom_point(aes(color = site, shape = till), size = 4) +
  scale_color_brewer(palette = "RdYlBu") +
  scale_x_reverse() +
  facet_wrap(facets = vars(site), scales = "free") +
  my_theme() + 
  theme(
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    axis.title.x = element_text(margin = margin(t = 8), size = 16),
    axis.title.y = element_text(margin = margin(r = 12), size = 16),
    strip.text = element_text(size = 16),
    legend.position = "none",
    aspect.ratio = 1
  ) +
  labs(
    y = "Organic Carbon (%)",
    x = "Anaerobe copies per g dry soil",
    shape = "Agricultural Use and Till",
    color = "Site"
  )

```

#### Statistics - unpublished

```{r}

anaerobe_c_sm_no_outlier <-
    lm(
    avg_perc_c ~ pc1_values, 
    data = 
      all_data %>% 
      filter(site == "SM") %>% 
      filter(!(till == "UN" & rep == 3))
  )

anaerobe_c_sm_no_outlier %>% summary()

```


# Variance Partitioning

## All sites

```{r}
varpart_perc_c <- 
      all_data %>% 
      arrange(rowid) %>% 
      select(-c(site, till, rep)) %>% 
      na.omit() %>% 
      pull(avg_perc_c)

varpart_data_perc_c <- 
  all_data %>% 
  arrange(rowid) %>% 
  mutate(
    cultivated = if_else(till == "UN", 0, 1),
    amended = if_else(amend == "A", 1, 0),
    red_no_till = if_else(till %in% c("NT", "MT"), 1, 0),
  ) %>% 
  select(
    -c(
      site, rep, sample, rowid, soil_order, amend
    )
  ) %>% 
  na.omit() 

```


### Check VIF

NOTE: highly co-linear variables have already been removed. 

```{r}

mineral.prot.lm <- 
  lm(
    varpart_perc_c
    ~ ssa_m2_g + 
      sro_mmol_kg,
    data = varpart_data_perc_c
  )

summary(mineral.prot.lm)

vif(mineral.prot.lm) 


```

```{r}

phys.prot.lm <- 
  lm(
    varpart_perc_c
    ~  till + 
      wsa_perc,
    data = varpart_data_perc_c
  )

summary(phys.prot.lm)

vif(phys.prot.lm) 


```



```{r}

climate.lm <-
  lm(
    varpart_perc_c
    ~ map_mm,
    data = varpart_data_perc_c
  )

summary(climate.lm)



```


```{r}
anaerobe.lm <-
  lm(
    varpart_perc_c
    ~ pc1_values_trans,
    #
    data = varpart_data_perc_c
  )

summary(anaerobe.lm)

varpart_data_perc_c

```

### Partition Variance - Supplementary Figure S7a

```{r}

total_c_mod <-
  varpart(
    varpart_perc_c,
    # Mineral protection - X1
    ~ ssa_m2_g + 
      sro_mmol_kg,
    # Physical Protection - X2
    ~ wsa_perc + till,
    # Climate - X3
    ~ map_mm,
    #Anaerobes - X4
    ~ pc1_values_trans,
    data = 
      varpart_data_perc_c,
    scale = FALSE 
  )

plot(
  total_c_mod,
  Xnames = c("Mineral", "Ag Use + Till", "Climate", "Anoxic"),
  id.size = 0.80
) 

```



### Test significance

```{r}
showvarparts(4)
```


## Cultivated only 

```{r}
varpart_perc_c_cult <- 
      all_data %>% 
      arrange(rowid) %>% 
      filter(till != "UN") %>% 
      select(-c(site, till, rep)) %>% 
      na.omit() %>% 
      pull(avg_perc_c)

varpart_data_perc_c_cult <- 
  all_data %>% 
  arrange(rowid) %>%
  filter(till != "UN") %>% 
  mutate(
    cultivated = if_else(till == "UN", 0, 1),
    amended = if_else(amend == "A", 1, 0),
    red_no_till = if_else(till %in% c("NT", "MT"), 1, 0),
  ) %>% 
  select(
    -c(
      site, rep, sample, rowid, soil_order, amend
    )
  ) %>% 
  na.omit() 
```

### Check VIF

```{r}

mineral.prot.lm.cult <- 
  lm(
    varpart_perc_c_cult
    ~ ssa_m2_g + 
      sro_mmol_kg,
    data = varpart_data_perc_c_cult
  )

summary(mineral.prot.lm.cult)

vif(mineral.prot.lm.cult) 

```

```{r}

phys.prot.lm.cult <- 
  lm(
    varpart_perc_c_cult
    ~ till + 
      wsa_perc,
    data = varpart_data_perc_c_cult
  )

summary(phys.prot.lm.cult)

vif(phys.prot.lm.cult) 


```


```{r}

climate.lm.cult <-
  lm(
    varpart_perc_c_cult
    ~ map_mm,
    #
    data = varpart_data_perc_c_cult
  )

summary(climate.lm.cult)



```


```{r}
anaerobe.lm.cult <-
  lm(
    varpart_perc_c_cult
    ~ pc1_values_trans,
    data = varpart_data_perc_c_cult
  )

summary(anaerobe.lm.cult)


```

### Partition Variance - Supplementary Figure S7b

```{r}
total_c_mod_cult <-
  varpart(
    varpart_perc_c_cult,
    # Mineral protection - X1
    ~ ssa_m2_g + 
      sro_mmol_kg,
    # Physical Protection - X2
    ~ wsa_perc + till,
    #X3 - Climate
    ~ map_mm,
    #Anaerobes - X4
    ~ pc1_values_trans,
    data = 
      varpart_data_perc_c_cult,
    scale = FALSE 
  )

plot(
  total_c_mod_cult,
  Xnames = c("Mineral", "Physical", "Climate", "Anoxic"),
  id.size = 0.8
) 



```

### Test Significance

What is testable?

```{r}

total_c_mod_cult

```

Is overall fit significant?

```{r}
rda.overall <- 
  rda(
    varpart_perc_c_cult ~ 
      ssa_m2_g + 
      sro_mmol_kg + 
      wsa_perc + 
      red_no_till +
      map_mm + 
      pc1_values_trans,
    data = 
      varpart_data_perc_c_cult,
    scale = FALSE 
  )

anova(rda.overall)
  
```

#### Significance tests for unique variance

Test whether the UNIQUE variance explained by each factor is significant

**Mineral**

```{r}

rda.mineral.part <- 
  rda(
      varpart_perc_c_cult ~ 
      ssa_m2_g +
      sro_mmol_kg +
      Condition(wsa_perc + till) + 
      Condition(map_mm) + 
      Condition(pc1_values_trans),
    data = varpart_data_perc_c_cult,
    scale = FALSE
  )

anova(rda.mineral.part)


```

**Physical**

```{r}

rda.phys.part <- 
  rda(
      varpart_perc_c_cult ~ wsa_perc + till +
      Condition(ssa_m2_g + sro_mmol_kg) +
      Condition(map_mm) + 
      Condition(pc1_values_trans),
    data = varpart_data_perc_c_cult,
    scale = FALSE
  )

anova(rda.phys.part)

```

**Climate**
```{r}

rda.climate.part <- 
  rda(
      varpart_perc_c_cult ~ map_mm + 
      Condition(wsa_perc + till) +
      Condition(ssa_m2_g + sro_mmol_kg) +
      Condition(pc1_values_trans),
    data = varpart_data_perc_c_cult,
    scale = FALSE
  )

anova(rda.climate.part)

```


**Anoxic**

```{r}

rda.anoxic.part <- 
  rda(
      varpart_perc_c_cult ~ pc1_values_trans +
      Condition(map_mm) + 
      Condition(wsa_perc + till) +
      Condition(ssa_m2_g + sro_mmol_kg),
    data = varpart_data_perc_c_cult,
    scale = FALSE
  )

anova(rda.anoxic.part)


```

