---
title: "PredictSoilC"
author: "Emily Lacroix"
date: "25 JAN 2023"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Set-up

## Load libraries

```{r message=FALSE}

library(MASS)
library(MuMIn)
library(car)
library(vegan)
library(psych)
library(readxl)
#library(lmerTest)
library(nlme)
library(outliers)
library(tidyverse)

conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")


```
## Figure theme
```{r}
my_theme <- function(base_size = 13, base_family = ""){ ## Control base font face and size. use `rel()` for relative font size.
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.border = element_rect(colour = "black", fill = "transparent"),
      panel.background  = element_blank(),
      panel.grid = element_blank(),
      strip.background = element_blank(),
      strip.text = element_text(size = 11),
      strip.text.y = element_text(size = 11)
    )
}

```


## Labels
```{r}

site_labels <- 
  c(
    "CREC" = "Carrington, ND",
    "GR" = "Novelty, MO",
    "SM" = "Crossville, AL",
    "WO" = "Wooster, OH"
  )

till_labels <- 
  c(
    "UN" = "Uncultivated",
    "NT" = "No-till",
    "MT" = "Minimum till",
    "CT" = "Conventional till"
  )

```

## File names

```{r eval=FALSE}

all_data_excel <- "AllData_03AUG.xlsx"

```

```{r eval=TRUE, echo=FALSE}

all_data_excel <- "/Users/elacroi3/Documents/Research/SHI/Data/DataCompilation/AllData_03AUG.xlsx"

```

## Import
```{r message=FALSE}

mineral <- 
  all_data_excel %>% 
  read_xlsx(sheet = "mineral_protection") %>% 
  select(-c(ssa_analysis_date)) %>% 
  separate(sample, into = c("site", "till", "amend", "rep")) %>% 
  mutate(
    landscape_position = if_else(site == "GR", amend, NA_character_),
    across(amend, ~if_else(site == "GR", "U", .)),
    across(rep, as.numeric)
  )

sixteenS_abund <-
  all_data_excel %>% 
  read_xlsx(sheet = "dna_ddpcr", na = "NA") %>% 
  distinct(site, till, amend, landscape_position, rep, copies_per_g_sixteenS)

anaerobe_copies_total <- 
  all_data_excel %>% 
  read_xlsx(sheet = "anaerobe_copies", na = "NA") %>% 
  add_row( #adding blank rows for GR-NT-F for now
    site = "GR",
    till = "NT",
    amend = "U",
    landscape_position = "F",
    rep = c(1,3),
    anaerobe_copies_per_g = NA_real_
  )

climate <- 
  all_data_excel %>% 
  read_xlsx(sheet = "climate", na = "NA") %>% 
  rename(rep = field_rep)


root_mass_bd <-
  all_data_excel %>% 
  read_xlsx(sheet = "gravimetric", na = "NA") %>% 
  mutate(
    avg_plant_mass_per_cm3 = plant_mass_2_mm / volume_cm3
  ) %>% 
    group_by(site, till, amend, landscape_position, field_rep) %>% 
    summarise(
      avg_plant_mass_per_cm3 = mean(avg_plant_mass_per_cm3, na.rm = TRUE),
      avg_bd = mean(bd, na.rm = TRUE)
    ) %>% 
  rename(rep = field_rep)


c_n <- 
  all_data_excel %>% 
  read_xlsx(sheet = "c_n", na = "NA") %>%
  rename(
    amend = amend_pos,
    rep = field_rep
  ) %>% 
  mutate(
    landscape_position = if_else(site == "GR", amend, NA_character_),
    across(amend, ~if_else(site == "GR", "U", .)),
  )


anaerobe_matrix <- 
  all_data_excel %>% 
  read_xlsx(sheet = "dna_ddpcr", na = "NA") %>% 
  group_by(
    site, till, amend, landscape_position, rep, target_gene
  ) %>% 
  summarise(
    copies_per_g = mean(copies_per_g, na.rm = TRUE),
    prop = mean(prop, na.rm = TRUE)
  ) %>% 
  pivot_wider(
    id_cols = c(site, till, amend, landscape_position, rep),
    names_from = target_gene,
    values_from = c(copies_per_g, prop)
  )

aggregate_est <- 
  all_data_excel %>% 
  read_xlsx(sheet = "agg_est") %>% 
  select(site, till, amend, landscape_position, rep, wsa_perc)


```

## Check for outliers in anaerobe data
```{r}
outliers <- grubbs.test(anaerobe_copies_total$anaerobe_copies_per_g)

outliers

outliers_low <- grubbs.test(anaerobe_copies_total$anaerobe_copies_per_g, opposite = TRUE)

outliers_low
```

## Join it all together 

This data:

* combines all of the imported data
* removes the WO-UN-U-2 outlier (which was also removed from `ddPCR.Rmd`)
* removes GR samples that have incomplete anaerobe abundances due to droplet generation errors for select genes

```{r}

all_data <- 
  mineral %>% 
  left_join(
    sixteenS_abund, 
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    anaerobe_copies_total,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    climate,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    root_mass_bd,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    c_n,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    anaerobe_matrix,
    by = c("site", "till", "amend", "landscape_position", "rep")
  ) %>% 
  left_join(
    aggregate_est,
    by = c("site", "till", "amend", "landscape_position", "rep")  
  ) %>% 
  filter(!(site == "GR" & landscape_position == "F" & rep %in% c(1,3))) %>% 
  rowid_to_column() %>% 
  arrange(site, till, amend, landscape_position, rep) %>% 
  ungroup() %>% 
  select(-landscape_position) %>% 
  na.omit() %>% 
  mutate(
    across(till, ~factor(., levels = c("UN", "NT", "MT", "CT"))),
    across(amend, ~factor(., levels = c("U", "A"))),
  ) %>%
  filter(
    sample != "WO-UN-U-2"
  )

```

# Supp Table: Soil Properties

```{r message=FALSE}

soil_properties <-
  all_data %>% 
  group_by(site, till, amend) %>% 
  summarise(
    across(
      c(
        avg_bd, 
        avg_perc_c, 
        avg_perc_n, 
        avg_plant_mass_per_cm3, 
        perc_clay, 
        ssa_m2_g, 
        sro_mmol_kg, 
        npoc_mg_c_g_soil, 
        plant_avail_n_ppm, 
        wsa_perc
      ),
      list(mean = mean, se = ~sd(.)/sqrt(n()))
    )
  )

```


# Regression

## All sites

```{r}

multiple_reg_data_c <-
  all_data %>% 
  mutate(
    cultivated = if_else(till == "UN", 0, 1),
    amended = if_else(amend == "A", 1, 0),
    red_no_till = if_else(till %in% c("NT", "MT"), 1, 0),
  ) %>% 
  select(
    -c(
      rowid, 
      sample, 
      amend,
      starts_with("prop"),
      copies_per_g_dsrAB,
      copies_per_g_gltA,
      copies_per_g_mcrA,
      copies_per_g_nirK,
      copies_per_g_nirS,
      soil_order,
      rep,
      count,
      gdd0,
      gdd10,
      precip_in_7,
      precip_in_14,
      precip_in_10,
      al_mmol_kg,
      fe_mmol_kg,
      mn_mmol_kg,
      plant_avail_n_ppm,
      npoc_mg_c_g_soil,
      avg_perc_n, #just playing around with removal
      map_mm, #removed after inspecting for VIF > 5
      mean_wfps  #removed after inspecting for VIF > 5
      )
  )

multiple_reg_data_c

```


### Simple linear regression, anaerobe copies vs. C

```{r}
anaerobe_c <- lm(avg_perc_c ~ anaerobe_copies_per_g, data = multiple_reg_data_c)


summary(anaerobe_c)
```


```{r message=FALSE}

all_data %>% 
  mutate(
    across(till, ~factor(., labels = till_labels)),
    across(site, ~factor(., labels = site_labels))
  ) %>% 
  ggplot(aes(x = anaerobe_copies_per_g, y = avg_perc_c)) + 
  geom_smooth(method = "lm", se = FALSE, color = "darkgray", linetype = 1) +
  geom_point(aes(color = site, shape = till), size = 4) +
  scale_color_brewer(palette = "RdYlBu") +
  my_theme() + 
  theme(
    aspect.ratio = 1,
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title.x = element_text(margin = margin(t = 8), size = 14),
    axis.title.y = element_text(margin = margin(r = 12), size = 14),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "top",
    legend.box = "vertical"
  ) +
  labs(
    y = "Total Organic Carbon (%)",
    x = "Anaerobe copies per g dry soil",
    shape = "Agricultural Use and Till",
    color = "Site"
  )


```

### Mixed-effects model 

```{r}

anaerobe_c_mixed_effects <-   
  lme(avg_perc_c ~ anaerobe_copies_per_g, 
      random = ~1|site, 
      data = multiple_reg_data_c
  )

summary_mixed_effects <- anaerobe_c_mixed_effects %>% summary()

summary_mixed_effects$tTable

r.squaredGLMM(anaerobe_c_mixed_effects)

```

## Individual sites

### Check for outliers in individual site sets

```{r}

crec_data <- 
  all_data %>% 
  filter(site == "CREC")

grubbs.test(crec_data$anaerobe_copies_per_g)
grubbs.test(crec_data$avg_perc_c)

wo_data <- 
  all_data %>% 
  filter(site == "WO")

grubbs.test(wo_data$anaerobe_copies_per_g)
grubbs.test(wo_data$avg_perc_c)


gr_data <- 
  all_data %>% 
  filter(site == "GR")

grubbs.test(gr_data$anaerobe_copies_per_g)
grubbs.test(gr_data$avg_perc_c)

sm_data <- 
  all_data %>% 
  filter(site == "SM")

grubbs.test(sm_data$anaerobe_copies_per_g)
grubbs.test(sm_data$avg_perc_c)


```

```{r}
sm_data_no_outliers <-
  sm_data %>% 
  filter(!(till == "UN" & rep == 3))


grubbs.test(sm_data_no_outliers$anaerobe_copies_per_g)
grubbs.test(sm_data_no_outliers$avg_perc_c)

```

### regressions WITH outlier in SM

```{r message=FALSE}
all_data %>% 
  mutate(
    across(till, ~factor(., labels = till_labels)),
    across(site, ~factor(., labels = site_labels))
  ) %>% 
  ggplot(aes(x = anaerobe_copies_per_g, y = avg_perc_c)) + 
  geom_smooth(method = "lm", se = FALSE, color = "darkgray", linetype = 1) +
  geom_point(aes(color = site, shape = till), size = 4) +
  scale_color_brewer(palette = "RdYlBu") +
  facet_wrap(facets = vars(site), scales = "free") +
  my_theme() + 
  theme(
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    axis.title.x = element_text(margin = margin(t = 8), size = 16),
    axis.title.y = element_text(margin = margin(r = 12), size = 16),
    strip.text = element_text(size = 16),
    legend.position = "none",
    aspect.ratio = 1,
    
  ) +
  labs(
    y = "Total Organic Carbon (%)",
    x = "Anaerobe copies per g dry soil",
    shape = "Agricultural Use and Till",
    color = "Site"
  )

```


```{r}
anaerobe_c_crec <- 
  lm(
    avg_perc_c ~ anaerobe_copies_per_g, 
    data = all_data %>% filter(site == "CREC")
  )

anaerobe_c_wo <-
    lm(
    avg_perc_c ~ anaerobe_copies_per_g, 
    data = all_data %>% filter(site == "WO")
  )

anaerobe_c_gr <- 
    lm(
    avg_perc_c ~ anaerobe_copies_per_g, 
    data = all_data %>% filter(site == "GR")
  )

anaerobe_c_sm <-
    lm(
    avg_perc_c ~ anaerobe_copies_per_g, 
    data = all_data %>% filter(site == "SM" )
  )

summary(anaerobe_c_crec)
summary(anaerobe_c_wo)
summary(anaerobe_c_gr)
summary(anaerobe_c_sm)


```

### regressions WITHOUT outlier in SM

```{r message=FALSE}

all_data %>% 
  filter(!(till == "UN" & rep == 3)) %>% 
  mutate(
    across(till, ~factor(., labels = till_labels)),
    across(site, ~factor(., labels = site_labels))
  ) %>% 
  ggplot(aes(x = anaerobe_copies_per_g, y = avg_perc_c)) + 
  geom_smooth(method = "lm", se = FALSE, color = "darkgray", linetype = 1) +
  geom_point(aes(color = site, shape = till), size = 4) +
  scale_color_brewer(palette = "RdYlBu") +
  facet_wrap(facets = vars(site), scales = "free") +
  my_theme() + 
  theme(
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    axis.title.x = element_text(margin = margin(t = 8), size = 16),
    axis.title.y = element_text(margin = margin(r = 12), size = 16),
    strip.text = element_text(size = 16),
    legend.position = "none",
    aspect.ratio = 1
  ) +
  labs(
    y = "Total Organic Carbon (%)",
    x = "Anaerobe copies per g dry soil",
    shape = "Agricultural Use and Till",
    color = "Site"
  )

```


```{r}

anaerobe_c_sm_no_outlier <-
    lm(
    avg_perc_c ~ anaerobe_copies_per_g, 
    data = 
      all_data %>% 
      filter(site == "SM") %>% 
      filter(!(till == "UN" & rep == 3))
  )

anaerobe_c_sm_no_outlier %>% summary()

```

## Stepwise

```{r}
# Fit the full model 
full.model <- lm(avg_perc_c ~., data = multiple_reg_data_c %>% select(-c(site, cultivated)))

# Stepwise regression model
step.model <- stepAIC(full.model, direction = "backward", trace = FALSE)

summary(step.model)

vif(step.model)

```


# Variance Partioning

## All sites

```{r}
varpart_perc_c <- 
      all_data %>% 
      arrange(rowid) %>% 
      select(-c(site, till, rep)) %>% 
      na.omit() %>% 
      pull(avg_perc_c)

varpart_data_perc_c <- 
  all_data %>% 
  arrange(rowid) %>% 
  mutate(
    cultivated = if_else(till == "UN", 0, 1),
    amended = if_else(amend == "A", 1, 0),
    red_no_till = if_else(till %in% c("NT", "MT"), 1, 0),
  ) %>% 
  select(
    -c(
      site, rep, sample, rowid, soil_order, amend
    )
  ) %>% 
  na.omit() 

```


### Check VIF

NOTE: highly co-linear variables have already been removed. 

```{r}

mineral.prot.lm <- 
  lm(
    varpart_perc_c
    ~ ssa_m2_g + 
      sro_mmol_kg,
    data = varpart_data_perc_c
  )

summary(mineral.prot.lm)

vif(mineral.prot.lm) 


```

```{r}

phys.prot.lm <- 
  lm(
    varpart_perc_c
    ~  till + 
      wsa_perc,
    data = varpart_data_perc_c
  )

summary(phys.prot.lm)

vif(phys.prot.lm) 


```



```{r}

climate.lm <-
  lm(
    varpart_perc_c
    ~ map_mm,
    data = varpart_data_perc_c
  )

summary(climate.lm)



```


```{r}
anaerobe.lm <-
  lm(
    varpart_perc_c
    ~ anaerobe_copies_per_g,
    #
    data = varpart_data_perc_c
  )

summary(anaerobe.lm)


```

### Partition Variance

```{r}

total_c_mod <-
  varpart(
    varpart_perc_c,
    # Mineral protection - X1
    ~ ssa_m2_g + 
      sro_mmol_kg,
    # Physical Protection - X2
    ~ wsa_perc + till,
    # Climate - X3
    ~ map_mm,
    #Anaerobes - X4
    ~ anaerobe_copies_per_g,
    data = 
      varpart_data_perc_c,
    scale = FALSE 
  )

plot(
  total_c_mod,
  Xnames = c("Mineral", "Ag Use + Till", "Climate", "Anoxic"),
  id.size = 0.80
) 

```

### Test significance

```{r}
showvarparts(4)
```


## Cultivated only 

```{r}
varpart_perc_c_cult <- 
      all_data %>% 
      arrange(rowid) %>% 
      filter(till != "UN") %>% 
      select(-c(site, till, rep)) %>% 
      na.omit() %>% 
      pull(avg_perc_c)

varpart_data_perc_c_cult <- 
  all_data %>% 
  arrange(rowid) %>%
  filter(till != "UN") %>% 
  mutate(
    cultivated = if_else(till == "UN", 0, 1),
    amended = if_else(amend == "A", 1, 0),
    red_no_till = if_else(till %in% c("NT", "MT"), 1, 0),
  ) %>% 
  select(
    -c(
      site, rep, sample, rowid, soil_order, amend
    )
  ) %>% 
  na.omit() 
```

### Check VIF

```{r}

mineral.prot.lm.cult <- 
  lm(
    varpart_perc_c_cult
    ~ ssa_m2_g + 
      sro_mmol_kg,
    data = varpart_data_perc_c_cult
  )

summary(mineral.prot.lm.cult)

vif(mineral.prot.lm.cult) 

```

```{r}

phys.prot.lm.cult <- 
  lm(
    varpart_perc_c_cult
    ~ till + 
      wsa_perc,
    data = varpart_data_perc_c_cult
  )

summary(phys.prot.lm.cult)

vif(phys.prot.lm.cult) 


```


```{r}

climate.lm.cult <-
  lm(
    varpart_perc_c_cult
    ~ map_mm,
    #
    data = varpart_data_perc_c_cult
  )

summary(climate.lm.cult)



```


```{r}
anaerobe.lm.cult <-
  lm(
    varpart_perc_c_cult
    ~ anaerobe_copies_per_g,
    data = varpart_data_perc_c_cult
  )

summary(anaerobe.lm.cult)


```

### Partition Variance

```{r}
total_c_mod_cult <-
  varpart(
    varpart_perc_c_cult,
    # Mineral protection - X1
    ~ ssa_m2_g + 
      sro_mmol_kg,
    # Physical Protection - X2
    ~ wsa_perc + till,
    #X3 - Climate
    ~ map_mm,
    #Anaerobes - X4
    ~ anaerobe_copies_per_g,
    data = 
      varpart_data_perc_c_cult,
    scale = FALSE 
  )

plot(
  total_c_mod_cult,
  Xnames = c("Mineral", "Physical", "Climate", "Anoxic"),
  id.size = 0.8
) 

```

### Test Significance

What is testable?

```{r}

total_c_mod_cult

```

Is overall fit significant?

```{r}
rda.overall <- 
  rda(
    varpart_perc_c_cult ~ 
      ssa_m2_g + 
      sro_mmol_kg + 
      wsa_perc + 
      red_no_till +
      map_mm + 
      anaerobe_copies_per_g,
    data = 
      varpart_data_perc_c_cult,
    scale = FALSE 
  )

anova(rda.overall)
  
```

#### Significance tests for unique variance

Test whether the UNIQUE variance explained by each factor is significant

**Mineral**

```{r}

rda.mineral.part <- 
  rda(
      varpart_perc_c_cult ~ 
      ssa_m2_g +
      sro_mmol_kg +
      Condition(wsa_perc + till) + 
      Condition(map_mm) + 
      Condition(anaerobe_copies_per_g),
    data = varpart_data_perc_c_cult,
    scale = FALSE
  )

anova(rda.mineral.part)


```

**Physical**

```{r}

rda.phys.part <- 
  rda(
      varpart_perc_c_cult ~ wsa_perc + till +
      Condition(ssa_m2_g + sro_mmol_kg) +
      Condition(map_mm) + 
      Condition(anaerobe_copies_per_g),
    data = varpart_data_perc_c_cult,
    scale = FALSE
  )

anova(rda.phys.part)

```

**Climate**
```{r}

rda.climate.part <- 
  rda(
      varpart_perc_c_cult ~ map_mm + 
      Condition(wsa_perc + till) +
      Condition(ssa_m2_g + sro_mmol_kg) +
      Condition(anaerobe_copies_per_g),
    data = varpart_data_perc_c_cult,
    scale = FALSE
  )

anova(rda.climate.part)

```


**Anoxic**

```{r}

rda.anoxic.part <- 
  rda(
      varpart_perc_c_cult ~ anaerobe_copies_per_g +
      Condition(map_mm) + 
      Condition(wsa_perc + till) +
      Condition(ssa_m2_g + sro_mmol_kg),
    data = varpart_data_perc_c_cult,
    scale = FALSE
  )

anova(rda.anoxic.part)


```

